Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-06 WSSSPE1_report/WSSSPE1_summary_report.tex
bullet list of what we want to discuss in use-cases

Perhaps discuss sustained software use-cases and issues surrounding
them. Following is a list of software projects discussed throughout the workshop:

@@

\note{Dan: do we need this section?  I think there's some overlap
  between this and the discussion in the Developing and Support
  Software section.  Or perhaps this should go in the cross-cutting
  issues section?  Let's write it down here - then we can decide if it goes elsewhere}

>>>>

Following is a list of software projects discussed throughout the workshop:

@@

In this section, we discuss the following:
\begin{itemize}
    \item Categorize the real-world software projects into workshop themes. This is based on the aspect of a software project that dominates and best fits one of the workshop themes.
    \item Discuss how the theme has impacted software projects over its lifetime.
    \item Discuss similarities and differences between these projects.
    \item What is a takeaway for a new project? What are the lessons learned? How can the course of current and future development projects be altered to implement lessons learned.
\end{itemize}

\note{Dan: do we need this section?  I think there's some overlap
  between this and the discussion in the Developing and Support
  Software section.  Or perhaps this should go in the cross-cutting
  issues section?  Let's write it down here - then we can decide if it goes elsewhere}
\note{Ketan: yes, may be this section will split and merge into other sections}
